Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 overview.tex
added some text in overview and some cites

\subsection{Testing distributed systems}
\label{sec:overview:bugs}

@@

There are two types of properties that developers of distributed systems are mostly interested in testing: \emph{safety} and \emph{liveness} properties. A safety property holds if it is \emph{always} satisfied, i.e. holds invariantly in every program state during execution. Likewise, a liveness property holds if it becomes \emph{eventually} satisfied, i.e. it will hold at some program state during execution. A safety or liveness property violation means that there is a bug that should be fixed.

Examples ...

>>>>

@@

There are two types of bugs that developers of distributed systems are mostly interested in finding: \emph{safety} and \emph{liveness} property violations~\cite{lamport1977proving}.

\begin{description}
\item[Safety] A safety property checks that an erroneous program state is \emph{never} reached, and is satisfied if it \emph{always} holds in each possible program execution.

\item[Liveness] A liveness property checks that some progress \emph{will} happen, and is satisfied if it \emph{always eventually} holds in each possible program execution.
\end{description}

\noindent
A safety property can be specified using an \emph{assertion} that fails if the property gets violated in some program state. As an example, in Azure Storage vNext we assert that whenever a message gets dequeued there must be an action that can handle the received message. Note that this safety property is not specific to Azure Storage vNext, and can be used in any system based on message passing.

Example of liveness bug in Azure Storage vNext.

Liveness properties are much harder to specify and check since they apply over entire program executions and not just individual program states. Normally, liveness checking requires the identification of an infinite fair execution that never satisfies the liveness property~\cite{schuppan2004efficient, musuvathi2008fair}. Prior work~\cite{schuppan2004efficient} has proposed that assuming a program with finite state space, a liveness property can be converted into a safety property. Other researchers proposed the use of heuristics and exploring finite executions of an infinite state space system using random walks to identify if a liveness property is satisfied~\cite{killian2007life}.
